Pattern matching for\\ $(213,231)$-avoiding permutations

### 2015-02-09 article.tex
end cases

\section{Pattern Matching With Bivincular Motif Avoiding (231,213)}	
\label{section:bivincular}

This section gives an algorithm to detect bivincular permutation in polynomial time in the case where the motif avoid $(213,231)$.
We denote $\pbmotif=\bmotif$ the bivincular motif.

\begin{proposition}
Let $\pbmotif$ be a bivincular motif such that $\pmotif$
avoid (231,213), 
$\ptext$ a permutation,
we can decide in $O(|\pmotif||\ptext|^3)$ time
and $O(|\ptext|^3)$ space
if $\pbmotif$
appear in $\ptext$.
\end{proposition}

@@

$
\PM{\pbmotif}{\ptext}{\min}{\max}{i}{j}=
\begin{cases}
	true 	& \text{If $\pbmotif[i:]$ is a motif of $\ptext[j:]$}\\
			& \text{with every element in}\\ 
			&[\min,\max]\\

@@

\end{proof}

>>>>

\section{$(213,231)$-avoiding bivincular patterns}
	\label{section:bivincular}

		This section is devoted to presenting a polynomial-time algorithm for deciding whether
	a $(213,231)$-avoiding bivincular pattern occurs in a permutation.

	\begin{proposition}
		\label{Proposition:bivincular pattern}
			Let $\sigma$ be a $(213,231)$-avoiding bivincular pattern of length $k$
			and $\pi \in S_n$.
			One can decide in $O(kn^3)$ time
			and $O(kn^3)$ space if $\pi$ contains $\sigma$.
	\end{proposition}

@@

$
\PM{\pbmotif}{\ptext}{\min}{\max}{i}{j}=
\begin{cases}
	true 	& \text{If $\pbmotif[i:]$ is a motif of $\ptext[j:]$}\\
			& \text{with every element in}\\
			&[\min,\max]\\
>>>>>>> f9bc0a20a19c155782e9e48e9d01a9fb6f3718ac

@@

\end{proof}
>>>>>>> f9bc0a20a19c155782e9e48e9d01a9fb6f3718ac
